Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-05-08 document/ms.tex
notes about implicit priors

Erik Petigura and collaborators (\citealt{petigura-a,petigura}) heroically
determined the empirical end-to-end completeness of their transit search
pipeline by injecting synthetic signals of known period and radius into the
raw aperture photometry and testing recovery rates.
They also published a catalog of XXX small planet candidates around G type
stars; YYY of them previously unknown.
Given the unprecedented quality of the completeness characterization, we will
focus on this dataset in this \paper.

We use all the injected samples from \citet{petigura} to compute the mean
(marginalized) detection efficiency in bins of $\ln\period$ and $\ln\radius$.
In each bin, this efficiency is simply the fraction of recovered injections.
For the purposes of this \paper, we will neglect the uncertainties introduced
by the fact that this estimate is being made with a finite number of samples.

The largest injected radius is $16\,R_\oplus$ but, because of the measurement
uncertainties on the radii, it will be necessary for us to model the
distribution to larger radii.
To do this, we approximate the survey completeness for $\radius>16\,R_\oplus$
as 1.

>>>>

Using an independent exoplanet search and characterization pipeline,
\citet{petigura} published a catalog of 603 planet candidates orbiting stars
in their ``Sun-like'' sample of \kepler\ targets.
For each candidate, \citet{petigura} used Markov chain Monte Carlo to sample
the posterior probability density---presumably assuming uniform priors---for
the radius ratio, transit duration, and impact parameter.
They then incorporated the uncertainties in the stellar radius and published
constraints on the physical radii of their candidates.
The exact shape of the implied prior on planet radius depends on the assumed
priors on radius ratio and stellar radius but in the limit of a broad uniform
prior on each quantity, the implicit prior at small physical radius is
approximately uniform; this is the assumption that we make.

A huge benefit of this dataset is that Erik Petigura and collaborators
published a rigorous analysis the empirical end-to-end completeness of their
transit search pipeline.
Instead of choosing a functional form for the detection efficiency of the
pipeline as a function of the parameters of interest, \citet{petigura}
injected synthetic signals of known period and radius into the raw aperture
photometry and determining the empirical recovery rate after the full analysis.

We use all the injected samples from \citet{petigura} to compute the mean
(marginalized) detection efficiency in bins of $\ln\period$ and $\ln\radius$.
In each bin, this efficiency is simply the fraction of recovered injections.
For the purposes of this \paper, we neglect the counting uncertainties
introduced by the finite number of samples.

The largest injected signal had a radius of $16\,R_\oplus$ but, because of the
measurement uncertainties on the radii, we need to model the distribution at
larger radii.
To do this, we approximate the survey completeness for $\radius>16\,R_\oplus$
as 1.

Given our domain knowledge of how detection efficiency depends on the physical
parameters, it might seem silly to measure the survey completeness in period
and radius instead of radius ratio or signal-to-noise.
It is also likely that a change of coordinates would yield a higher precision
result.
That being said, it is still correct to measure the completeness in period and
radius, and there are a few practical reasons for our choice.
First, since the radius uncertainties are dominated by uncertainties in the
stellar parameters, it is not possible to use the published catalog
(\citealt{petigura}) to compute constraints on radius ratios.
\dfmtodo{finish this}
